---
title: "Linear Reg model for mtcars"
output: html_notebook
---
 
#Install Packages & run Libraries
```{r}
#install.packages('Metrics')
library(corrplot)
library(dplyr)
```

#Assign mtcars to mtcars_model
```{r}
mtcars_model = mtcars
```

#Genarate model with data mtcars_model for mpg against other parameters
```{r}
model = lm(mpg ~ ., data = mtcars_model)
```

#Summary of the model generated
```{r}
summary(model)
```

#Correlation for mtcars_model
```{r}
cor(mtcars_model)
mtcars_model %>%  select_if(is.numeric) %>% cor() %>% corrplot()
```

#Identify Training & Test dataset from mtcars_model
```{r}
set.seed(723)

index <- sample(1:nrow(mtcars_model),round(nrow(mtcars_model) * 0.7))

train <- mtcars_model[index,]

test <- mtcars_model[-index,]
```

#Assign test dataset values to test_p eliminating mpg
```{r}
test_p <- test %>%  select(-one_of('mpg'))
```

#Genarate best fit model
```{r}
model = lm(mpg ~  wt + qsec + am  + carb, data = mtcars_model)

summary(model)
```

#Predict the value mpg using model & display the predicted value
```{r}
predicted <- predict(model,test_p)

predicted
```

#calculate Mean Absolute Error & Root Mean Sq Error values
```{r}
mean(abs(test$mpg - predicted))

Metrics::rmse(test$mpg,predicted = predicted)
```



